### 2025-05-04 conteudo/background/linux.tex
add diff information

\todo[inline]{Not exactly on this section, but I need to mention GIT, as one of the similarity methods is based on the GIT command.}

>>>>

\subsection{Diff command}

The \textit{diff} command is a command line in Linux that allows the user to compare 
two files line by line \citep{diffcommand}. There are multiple forms 
that the results of the command can be shown, one example of the command being executed 
can be found in Figure \ref{fig:diff}. With the command results, it is easy to visualize and extract 
the number of lines that are equal and different between the two compared files.

\begin{figure}
\includegraphics[scale=0.3]{diff_command}
\caption{Example of \textit{diff} command executed}
File 1 content is shown in red and file 2 content is shown in green. \textit{-} 
represents a line that only exist in file 1, \textit{+} represents a line that only exist in file 2,
\textit{!} represents a line that exist in both file but has modifications between them, and empty on the
start of a line represents that the line exist in both files without any modifications.
\label{fig:diff}
\end{figure}

We use thhe \textit{diff} command as the base of one of the code duplication detection methods 
on the tool proposed on this work, although it is not extensive explored as the text similarity
method for code duplication detection.
